Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection

### 2021-04-07 publication_materials/ms_rbc.tex
abstract rev2a

\begin{abstract}
A novel quasilinear form of the Boussinesq Rayleigh-B\'enard equations is derived from the classical linear stability analysis. Eigenfunction amplitudes are obtained by requiring marginal-stability. Symmetric thermally-equilibrated states are then obtained and their properties are analyzed. Such states are compared with statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulations; marginally-stable thermally-equilibrated states have thinner boundary layers which scale like $\delta \sim Ra^{-1/3}$. 2-dimensional simulations are initialized with solutions to the quasilinear problem;
they do not undergo a convective transient period but turn out to be kinetically exaggerated.
\end{abstract}

>>>>

\begin{abstract}
Reduced models give us some understanding of the behavior of complicated systems. We derive a quasilinear form of the Boussinesq Rayleigh-B\'enard equations from the classical linear stability analysis. Eigenfunction amplitudes are obtained by requiring marginal-stability. We obtain symmetric thermally-equilibrated states and analyze their properties. Such states are compared with statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulations; marginally-stable thermally-equilibrated states have thinner boundary layers and larger Nusselt numbers $\Nu$ which scale like $\Nu \sim Ra^{1/3}$. We initialize 2-dimensional simulations with solutions to the quasilinear problem;
they do not undergo a convective transient period but turn out to be kinetically exaggerated.
\end{abstract}
